Cross Validation Approaches for Penalized Cox Regression

### 2019-03-20 main.tex
Some edits to Section 3

Simulation studies were conducted to compare how those methods behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. \bnote{Covariate matrix $X$ with $n$ observations and $p$ covariates is generated from independent $\text{Normal}(0, 1)$ samples; and coefficient vector $\beta$ is sparse, with most entries equal to zero. Given $X$ and $\beta$, survival times were generated from exponential distribution with rate parameter set to be $\exp(X\beta)$.} Censoring status indicators were drawn independently from the binomial distribution. All simulations were implemented in R \citep{R}. We varied the sample size, dimension, censoring percentage and signal strength of the simulated data sets to examine how these factors affect the performance of cross-validation.

@@

Throughout, we communicate the estimation accuracy in terms of relative MSE, as compared to the oracle model.  For each generated data set, an oracle model was fit using Cox regression only including the variables with non-zero coefficients. Letting $\hat{\beta}^{oracle}$ denote the resulting estimates, the relative MSE, on the log scale, is given by
\begin{equation}
\log\left\{ \frac{\MSE(\hat{\beta}(\lambda^{\text{cv}}))}{\MSE(\hat{\beta}^{\text{oracle}})} \right\},
\end{equation}
where $\lambda^{cv}$ denotes the value of $\lambda$ selected by cross-validation.   These results are then averaged over N replications; the $\log$ of the ratio is taken to correct for skewness. \bnote{clarification: MSE is estimated by avevaring across N replications respectively for $\hat{\beta}(\lambda^{cv})$ and $\hat{\beta}^{oracle}$. The ratio and $\log$ were taken afterwards }

@@

\bnote{I rewrote this paragraph} For each simulated data set, the covariate matrix has $n = 120$ observations and $p = 1000$ covariates. The covariate vector $\beta$ is assumed to have sparsity, where $\beta_j = 0$ for $j \in \{11,12,..,1000\}$. Then for $j \in \{1,2, ..., 10 \}$, $\beta_j = s$, where $s$ is a prespecified constant that finetunes the signal strength in the simulated data set. In the first simulation study, we varied $s$ from 0.4 to 0.9. The survival outcomes have 10$\%$ expected censoring. For each of the four methods described in Section~\ref{Sec:methods}, 10-fold cross-validation was implemented. $N = 200$ replications were used for each scenario.

\begin{figure}[ht]
  \centering
  \includegraphics[height= 7cm ]{./manuscript_figure/figure_2_new.png}
  \caption{\label{Fig:mse-brier-c} Simulation comparing 4 CV methods. The horizontal axis in all three plots is $s$, which represents the signal strength in the data. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier Scores is plotted in the middle. Out-of-sample Harrell's C Index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$. \bnote{behavior of the deviance residual approach has slightly changed}} 
\end{figure}

>>>>

Simulation studies were conducted to compare how the methods described in Section~\ref{Sec:methods} behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. For these simulation studies, the covariate matrix $X$, consisting of $n$ observations and $p$ covariates, was generated from independent $\text{Normal}(0, 1)$ samples. Given $X$ and a coefficient vector $\beta$, survival times were generated from exponential distribution with rate parameter $\exp(X\beta)$. Censoring status indicators were drawn independently from the binomial distribution. All simulations were implemented in R \citep{R}. We varied the sample size, dimension, censoring percentage and signal strength of the simulated data sets to examine how these factors affect the performance of cross-validation.

@@

Throughout, we communicate the estimation accuracy in terms of relative MSE, as compared to the oracle model.  For each generated data set, an oracle model was fit using Cox regression only including the variables with non-zero coefficients. Letting $\hat{\beta}^{oracle}$ denote the resulting estimates, the relative MSE, on the log scale, is given by
\begin{equation}
\log\left\{ \frac{\MSE(\hat{\beta}(\lambda^{\text{cv}}))}{\MSE(\hat{\beta}^{\text{oracle}})} \right\},
\end{equation}
where $\lambda^{cv}$ denotes the value of $\lambda$ selected by cross-validation.   These results are then averaged over N replications; the $\log$ of the ratio is taken to correct for skewness. \bnote{clarification: MSE is estimated by avevaring across N replications respectively for $\hat{\beta}(\lambda^{cv})$ and $\hat{\beta}^{oracle}$. The ratio and $\log$ were taken afterwards } \note{I'm not sure why this is a note; shouldn't you rewrite the sentence?}

@@

\bnote{I rewrote this paragraph} For each simulated data set, the covariate matrix has $n = 120$ observations and $p = 1000$ covariates. The covariate vector $\beta$ is assumed to be sparse, with $\beta_j = 0$ for $j \in \{11,12,..,1000\}$ and $\beta_j = s$ for $j \in \{1,2, ..., 10 \}$, where $s$ is a prespecified constant that parameterizes the signal strength in the simulated data set. In the first simulation study, we varied $s$ from 0.4 to 0.9. The survival outcomes have 10$\%$ expected censoring. For each of the four methods described in Section~\ref{Sec:methods}, 10-fold cross-validation was implemented. $N = 200$ replications were used for each scenario.

\begin{figure}[ht]
  \centering
  \includegraphics[height= 7cm ]{./manuscript_figure/figure_2_new.png}
  \caption{\label{Fig:mse-brier-c} Simulation comparing 4 CV methods. The horizontal axis in all three plots is $s$, which represents the signal strength in the data. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier scores are plotted in the middle. Out-of-sample Harrell's C index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$. \note{I really think the x axis should be Signal (s) or Signal strength (s)}}
\end{figure}
